Lab 2 Draft Report: COVID-19 Case Rate vs Population and Policy

### 2020-12-01 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Update Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
model 3 update from model 2

Firstly, "mask_public_bool" column is created from "mask_public", with 1 represents that the state has a pulbic mask policy, and 0 means there's no explicit public mask policy from the state.

@@

```{r}
model3a <- lm(case_rate_100k ~ log10(population_density)
              + poverty_pct + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)
```

>>>>

Firstly, "mask_public_bool" column is created from "mask_public", with 1 represents that the state has a pubic mask policy, and 0 means there's no explicit public mask policy from the state.

@@

```{r}
model3a <- lm(case_rate_100k ~ senior_per_100k + log(population_density) 
              + noneld_pre_existing_per_100k + poverty_per_100k + white_per_100k 
              + unemployed_per_100k + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)

model3a <- lm(case_rate_100k ~ senior_per_100k + log(population_density) 
              + poverty_per_100k 
              + unemployed_per_100k + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)
```

CLM assumptions check for Model 3:
```{r}
#Zero Conditional Mean
plot(model3a, which=1)

#Normality of errors
plot(model3a, which=2)

#Homoskedasticity
plot(model3a, which=3)

#Collinearity
vif(model3a)>4
```
